Paper Figure Generation

### 2023-05-08 R/PaperFigureGeneration.rmd
Fixed incorrect figure title

### All timepoints together ###
# plotNucFreqVsReadLengthBarPlot(NHF1FivePrimeMismatchCPDNucFreqAllRepsTGFiltered, 
#                                title = "NHF1 CPD All Reps TG-Filtered 5' Anchored Nuc Freq",
#                                secondaryYAxisLabel = "3' Cut Site Distance",
#                                posType = FIVE_PRIME, showThreePrimeCutSite = TRUE,
#                                expansionOffset = 10, minReadLength = 1, maxReadLength = 8,
#                                xAxisLabel = "Mismatch Relative Position")
```
```{r figure_S7C, fig.width = 5, fig.height = 5}
### Just the 1h timepoint ###
plotPositionAcrossTimepointAndReadLength(NHF1CPDMismatchDataAllRepsTGGFiltered["1h"], includedTypes = c("C>T"),
                                         title = "NHF1 CPD 1h All Reps TG-Filtered C>T Mismatch Pos Freq",
                                         zScoreTables = NHF1CPDMMFreqZScoresAllRepsTGFiltered,
                                         posType = THREE_PRIME, yAxisLabel = "Relative C>T Frequency",
                                         xAxisBreaks = c(-1,-10,-20,-30))

>>>>

### All timepoints together ###
# plotNucFreqVsReadLengthBarPlot(NHF1FivePrimeMismatchCPDNucFreqAllRepsTGFiltered, 
#                                title = "NHF1 CPD All Reps TG-Filtered 5' Anchored Nuc Freq",
#                                secondaryYAxisLabel = "3' Cut Site Distance",
#                                posType = FIVE_PRIME, showThreePrimeCutSite = TRUE,
#                                expansionOffset = 10, minReadLength = 1, maxReadLength = 8,
#                                xAxisLabel = "Mismatch Relative Position")
```
```{r figure_S7C, fig.width = 5, fig.height = 5}
### Just the 1h timepoint ###
plotPositionAcrossTimepointAndReadLength(NHF1CPDMismatchDataAllRepsTGGFiltered["1h"], includedTypes = c("C>T"),
                                         title = "NHF1 CPD 1h All Reps TGG-Filtered C>T Mismatch Pos Freq",
                                         zScoreTables = NHF1CPDMMFreqZScoresAllRepsTGFiltered,
                                         posType = THREE_PRIME, yAxisLabel = "Relative C>T Frequency",
                                         xAxisBreaks = c(-1,-10,-20,-30))
